%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{General Automation Laboratory Technology} % Organization
{San Carlos, CA} % Location
{August 2020 - May 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Maintained, Refactored, and Debugged the core business application (multi-threaded WPF application) performing image analysis, instrument communication, and data storage/retrieval.}
\item {Implemented Poisson statistics calculator in C\# to dynamically determine dilution factor for getting a set number of bacterial isolates.}
\item {Implemented arbitrary picker tool in C\# for wells on micro-array chip for R\&D.}
\item {Investigated and prototyped algorithms for well selection and identification using Python and OpenCV in micro-array chips.}
\end{cvitems}
}

%------------------------------------------------    

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Whisper.ai} % Organization
{San Francisco, CA} % Location
{January 2020 - May 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Maintained a BuildKite server for the hardware CI/CD pipeline using Python and BASH.}
\item {Wrote Python unit tests to characterize and confirm the operation of several hearing aid features such as hour long audio playback tests.}
\end{cvitems}
}

%------------------------------------------------    

%------------------------------------------------

\cventry
{Systems Programmer} % Job title
{Prellis Biologics} % Organization
{San Francisco, CA} % Location
{January 2019 - January 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Patent (WO2020028431 - Methods and Systems for Three-Dimensional Printing) for software methods on holography based 3D printing.}
\item {Constructed and partitioned 3D STL model into optimal chunks for voxel based printing using two-photon absorption.}
\item {Used OpenCV in C++ to process images with morphological operators, k-means clustering, and apply software based optical correction.}
\item {Implemented, bench-marked, and optimized GPU accelerated computational holography pipeline using CUDA and OpenCV.}
\item {Implemented a watertight voxelization algorithm for very large and sparse 3D structures in C++.}
\item {Wrote a custom debugging tool to view and analyze large voxel structures with three.js.}
\item {Designed and implemented software for HolographX winning the Innovation Award at the Merck Technical Symposium.}
\end{cvitems}
}

%------------------------------------------------    


%------------------------------------------------

\cventry
{Electronic Systems Intern} % Job title
{Tesla} % Organization
{Palo Alto, CA} % Location
{June 2018 - September 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Analyzed factory data and made process recommendations to increase Radio Tuner FPY.}
\item {Created BASH tools to reduce required number of engineers on field tests by 50\%.}
\item {Designed and implemented radio test suite decreasing testing time by automating the test process using PyVisa.}
\item {Created a scalable service to run remote commands simultaneously on several engineering cars using BASH and TCL.}
\item {Designed and implemented a service for checking hardware/firmware/software compatibility of Radio OTA updates using BASH/TCL.}
 \end{cvitems}
}

%------------------------------------------------    



%------------------------------------------------
\cventry
{Wireless Hardware Intern} % Job title
{Tesla} % Organization
{Palo Alto, CA} % Location
{June 2017 - September 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Determined feasibility of In-Car wireless harness using Python and BASH.}
\item {Analyzed link between antenna placement and QoS in cars using Python and BASH.}
\item {Created RF test suite (Bluetooth, 802.11b/g/n, WCDMA, GSM, and LTE) using PyVisa.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Wireless Engineering Intern} % Job title
{Dolby Laboratories} % Organization
{San Francisco, CA} % Location
{June 2016 - September 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented automated tests for characterizing the Bluetooth performance and capabilities of a chipset using PyVisa.}
\item {Designed scripts to automate, perform and analyze wireless performance of a network using iPerf, Python, Bash, and MATLAB.}
\end{cvitems}
}

%------------------------------------------------


% \cventry
% {Undergraduate Researcher} % Job title
% {Applied Micro/Nano Electromagnetics Research Laboratory} % Organization
% {545 Bainer Hall Drive, Davis} % Location
% {January 2017 - February 2018} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {Performed simulations and tests in HFSS using Floquet's Theorem to determine a proper simulation and test procedure for measuring the S11 magnitude and phase of an infinite meta-surface using various unit cells in the Giga/Tera hertz range for satellite communications.}
% \end{cvitems} 
% }
\end{cventries}